---
title: "Cancer Tx patterns and pathway"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    theme : yeti
---

```{r global_packages}
library(flexdashboard)
library(shiny)
library(CancerTxPathway)
library(dplyr)
library(highcharter)
library(plotly)
```

Usage Patterns
================================

Inputs {.sidebar}
--------------------------------

### Annual Usage patterns in treatment regimen

The proportion of the patients number treated each regimen for total chemotherapy received patients.

```{r sidebar_ui}
inputPanel(
  sliderInput("yearThreshold", "Range of the year",min = 1970, max = 2020, value = c(1990,2020))
)

```


### Annual Usage patterns in treatment regimen

The proportion of the patients number treated each regimen for total chemotherapy received patients.

```{r sidebar_ui2}
inputPanel(
  sliderInput("yearThreshold", "Range of the year",min = 1970, max = 2020, value = c(1990,2020))
)

```

Row
-------------------------------------

### Treatment Pathway

```{r, echo=FALSE,fig.keep='all'}

treatmentPathway(connectionDetails,
                 cohortDatabaseSchema,
                 cohortTable,
                 outputFolder,
                 outputFileTitle,
                 conditionCohortIds,
                 targetCohortIds,
                 eventCohortIds = surgeryCohortIds,
                 minimumRegimenChange = 0,
                 treatmentLine,
                 collapseDates,
                 nodeMinSubject)
```

Row
-------------------------------------

### Usage patterns of the treatment

```{r}

fromYear <- reactive(input$yearThreshold[1])
toYear <- reactive(input$yearThreshold[2])
output$usage <- renderHighchart({
  usagePatternGraph(connectionDetails,
                    cohortDatabaseSchema,
                    cohortTable,
                    targetCohortIds,
                    conditionCohortIds,
                    outputFolder,
                    outputFileTitle,
                    fromYear(),
                    toYear())
  
})

highchartOutput('usage')

```

### Treatment Iteration Distribution

```{r, echo=FALSE,results='hide',fig.keep='all'}

heatmapPlotData<-heatmapData(connectionDetails,
                             cohortDatabaseSchema,
                             cohortTable,
                             targetCohortIds,
                             outputFolder,
                             outputFileTitle,
                             identicalSeriesCriteria,
                             conditionCohortIds)
treatmentIterationDistribution(heatmapPlotData,
                               maximumCycleNumber,
                               heatmapColor)
```

Event Incidence In Treatment Iteration
================================

Inputs {.sidebar}
--------------------------------

```{r sidebar_ui3}

textInput("ui2","Keyword","regimen")
actionButton("act","Change apply")


```

Column {data-width=600}
--------------------------------

### Chart 1

```{r, echo=FALSE,results='hide',fig.keep='all'}

renderPlot(cycleIncidencePlot(connectionDetails,
                   cohortDatabaseSchema,
                   cohortTable,
                   outputFolder,
                   outputFileTitle,
                   targetCohortIds,
                   conditionCohortIds,
                   eventCohortIds,
                   restrictInitialSeries = TRUE,
                   restricInitialEvent =TRUE,
                   identicalSeriesCriteria,
                   eventPeriod = 30,
                   targetMin))

```


Event Onset Timing
================================

Column {data-width=600}
--------------------------------

### Chart 2

```{r, echo=FALSE,fig.keep='all'}

renderPlotly(incidenceDatePlot(connectionDetails,
                  cohortDatabaseSchema,
                  cohortTable,
                  targetCohortIds,
                  outputFolder,
                  outputFileTitle,
                  identicalSeriesCriteria = 60,
                  conditionCohortIds,
                  eventCohortIds,
                  restrictEventDate = 90))

```   

About
================================

Copyright 2020 Observational Health Data Sciences and Informatics

This file is part of CancerTxPathway

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software
distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and
limitations under the License.
