---
title: "Cancer Tx patterns and pathway"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    theme : yeti
---

```{r global_packages}
library(flexdashboard)
library(shiny)
library(CancerTxPathway)
library(dplyr)
library(highcharter)
library(plotly)
library(viridis)
library(gridExtra)
library(scales)
library(hrbrthemes)
library(ggplot2)
```

Usage Patterns {data-orientation=rows}
================================

Row
-------------------------------------

### Treatment Pathway

```{r, echo=FALSE,fig.keep='all'}
fileNameNodes <- paste0(outputFileTitle,'_','SankeyNodes.csv')
fileNameLinks <- paste0(outputFileTitle,'_','SankeyLinks.csv')
nodesPath <- file.path(outputFolder, fileNameNodes)
linksPath <- file.path(outputFolder, fileNameLinks)
nodes<-read.csv(nodesPath,stringsAsFactors = F)
links<-read.csv(linksPath,stringsAsFactors = F)
networkD3::sankeyNetwork(Links = links, Nodes = nodes, Source = "source",Target = "target", Value = "value", NodeID = "name", fontSize = 12, nodeWidth = 30,sinksRight = FALSE)
```

Row
-------------------------------------

### Usage patterns of the treatment

```{r}

fileNameUsage <- paste0(outputFileTitle,'_','usagePatternRegimenProportion.csv')
UsagePath <- file.path(outputFolder, fileNameUsage)
plotData <- read.csv(UsagePath,stringsAsFactors = F)
plotData %>% highcharter::hchart(.,type="line",hcaes(x = Year,y=proportion,group = Cohort)) %>% hc_xAxis(title = list(text = "Year")) %>% hc_yAxis(title = list(text = "The number of patients treated specific regimen / Total patients received chemotherapy (%)"),from = 0, to =70)

```

### Treatment Iteration Distribution {.no-padding}

```{r, echo=FALSE,results='hide',fig.width=11,dpi = 100}

fileNameIteration<- paste0(outputFileTitle,'_','treatmentIterationDistribution.csv')
IterationPath <- file.path(outputFolder, fileNameIteration)
heatmapPlotData <- read.csv(IterationPath,stringsAsFactors = F)
total<-heatmapPlotData %>%group_by(cohortName) %>% mutate(sum = sum(n)) %>% select (cohortName,sum)
total<-unique(total)
total$label<-paste0(total$cohortName,' \n','(n = ',total$sum,')')

heatmapPlotDataN <- as_tibble(heatmapPlotData) %>% mutate(ratioLabel = paste0(ratio,'\n','(n = ',n,')')) %>%  select(cycle, cohortName, ratioLabel)%>% subset(cycle <=maximumCycleNumber)
plotDataN <- tidyr::spread(heatmapPlotDataN, cycle, ratioLabel)
plotDataN[is.na(plotDataN)] <- 0
plotDataN$cohortName <- NULL
#data pre-processing
heatmapPlotData <- as_tibble(heatmapPlotData) %>% select(cycle, cohortName, ratio) %>% subset(cycle <=maximumCycleNumber)
class(heatmapPlotData$ratio) = "dbl"
plotData <- tidyr::spread(heatmapPlotData, cycle, ratio)
plotDataNMatrix<-as.matrix(plotDataN)
sort.order <- order(plotDataNMatrix[,1])

plotData <- left_join(plotData,total,by = c("cohortName"="cohortName"))
plotData <- as.data.frame(plotData)
plotData[is.na(plotData)] <- 0

row.names(plotData) <- plotData$label
plotData$cohortName <- NULL
plotData$sum <- NULL
plotData$label <- NULL
sort.order <- order(plotData[,1])
label<-as.matrix(plotDataN)
superheat::superheat(plotData,
                     X.text = label,
                     X.text.size = 3,
                     scale = FALSE,
                     left.label.text.size=3,
                     left.label.text.alignment = "left",
                     left.label.size = 0.3,
                     bottom.label.text.size=4,
                     bottom.label.size = .05,
                     heat.pal = RColorBrewer::brewer.pal(9, heatmapColor),
                     heat.pal.values = c(seq(0,0.3,length.out = 8),1),
                     order.rows = sort.order,
                     title = "Trends of the treatment iteration")

```

Event Incidence In Treatment Iteration 
================================

Row {data-width = 600}
--------------------------------

### Incidence of the adverse event after each treatment iteration {data-vertical_layout=scroll}

```{r, echo=FALSE,results='hide',fig.keep='all',fig.width = 4,fig.height = 7, dpi = 100}

fileNameEventIncidenceInCycle<- paste0(outputFileTitle,'_','EventIncidenceInCycle.csv')
fileNameEventIncidenceInCyclePath <- file.path(outputFolder, fileNameEventIncidenceInCycle)
plotData <- read.csv(fileNameEventIncidenceInCyclePath,stringsAsFactors = F)
p1 <- ggplot(na.omit(plotData), aes(x = cohort_cycle, y = ratio, group = cohortName, color = cohortName)) +
  theme_bw() +
  scale_x_discrete(limits = na.omit(plotData)$cohort_cycle) +
  geom_point(size = 2, aes(fill = cohortName)) +
  geom_text(aes(label = percent(round(ratio, 2))),
            size = 4, hjust = -0.01, vjust = -0.2, fontface = "plain") +
  geom_smooth(size = 1.0, method = 'lm', aes(fill = cohortName)) +
  scale_fill_viridis(discrete=TRUE) +
  scale_color_viridis(discrete=TRUE) +
  theme(legend.position='none',
        plot.title = element_text(size=20, face="bold", vjust=2),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=13),
        axis.text = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        panel.border = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  labs(y = 'Incidence Rate')


# plot #2 - number of Incidence
p2 <- ggplot(na.omit(plotData), aes(x = cohort_cycle, group = cohortName, color = cohortName)) +
  theme_bw() +
  scale_x_discrete(limits = na.omit(plotData)$cohort_cycle) +
  geom_bar(aes(y = total, fill = cohortName), alpha = 0.2, stat = 'identity',show.legend = TRUE) +
  geom_bar(aes(y = event, fill = cohortName), alpha = 0.6, stat = 'identity',show.legend = FALSE) +
  geom_text(aes(y = total, label = paste(event,'/',total)),
            angle = 90, size = 4, hjust = -0.1, vjust = 0.4,check_overlap = TRUE,show.legend = FALSE, position = position_dodge(width = 0.6)) +
  geom_text(aes(y = 0, label = cycle), angle = 90, size = 4, hjust = 1.25, vjust = 0.4,check_overlap = TRUE,show.legend = FALSE) +
  scale_fill_viridis(discrete=TRUE) +
  scale_color_viridis(discrete=TRUE) +
  theme(legend.position='bottom',
        legend.title=element_blank(),
        plot.title = element_text(size=20, vjust=2),
        axis.title.x = element_text(size=13),
        axis.title.y = element_text(size=13),
        axis.text = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        panel.border = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  scale_y_continuous(limits = c(0, max(plotData$total * 1.1))) +
  labs(x = 'Iteration Number of treatment', y = 'Number of Incidence')

# multiplot
grid.arrange(p1, p2, ncol = 1)

```

Row {data-width = 500}
--------------------------------

### Adverse event onset timing after first treatment {data-vertical_layout=scroll}

```{r, echo=FALSE,fig.keep='all'}
fileNameEventIncidenceInDates<- paste0(outputFileTitle,'_','EventIncidenceInDates.csv')
fileNameEventIncidenceInDatesPath <- file.path(outputFolder, fileNameEventIncidenceInDates)
plotData <- read.csv(fileNameEventIncidenceInDatesPath,stringsAsFactors = F)
p <- ggplot(plotData,aes(x=cohortName, y=dateDiff)) +
  geom_violin(size=0.2,scale = 'width') +
  ggbeeswarm::geom_quasirandom(size = 1,aes(color = category))+
  scale_color_viridis(discrete=TRUE) + theme_ipsum() +
  theme(
    legend.position= 'bottom',legend.title=element_blank()
  ) +
  coord_flip() +
  xlab("") +
  ylab("Time from discharge (days)")

plotly::ggplotly(p) %>% layout(legend = list(orientation = 'h',y=-0.1,x=0))

```   

About
================================

Copyright 2020 Observational Health Data Sciences and Informatics

This file is part of CancerTxPathway

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software
distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and
limitations under the License.
